Equalizer\\Programming and User Guide

### 2010-12-10 Developer/ProgrammingGuide/paper.tex
Implement RFE 3132979: Add passive stereo detection to compound auto stereo mode
[ ] May break build
[ ] May break existing applications (see CHANGES.txt)
[ ] Bugfix
[x] New Feature
[x] Cleanup
[ ] Optimization
[x] Documentation

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_COMPOUND\_IATTR\_STEREO\_MODE\\
  \textbf{Value} & AUTO \textbar QUAD \textbar \ ANAGLYPH\\
  \textbf{Default} & AUTO\\
  \textbf{Details} & Selects the algorithm used for stereo
  rendering. QUAD-buffered stereo uses the left and right buffers of a
  stereo window (active stereo). Anaglyphic stereo uses
  \textsf{glColorMask} to mask colors for individual eye passes, used in
  conjunction with colored glasses. AUTO selects QUAD if the drawable is capable
  of active stereo rendering, otherwise ANAGLYPH is selected\\
  \hline
\end{tabularx}\\\vfill

>>>>

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_COMPOUND\_IATTR\_STEREO\_MODE\\
  \textbf{Value} & AUTO \textbar QUAD \textbar \ ANAGLYPH \textbar \ PASSIVE\\
  \textbf{Default} & AUTO\\
  \textbf{Details} & Selects the algorithm used for stereo
  rendering. QUAD-buffered stereo uses the left and right buffers of a stereo
  window (active stereo). Anaglyphic stereo uses \textsf{glColorMask} to mask
  colors for individual eye passes, used in conjunction with colored
  glasses. PASSIVE stereo never selects a stereo buffer of a quad-buffered
  drawable. AUTO selects PASSIVE if the left or right eye pass is not used, QUAD
  if the drawable is capable of active stereo rendering, and ANAGLYPH in all
  other cases.
  \hline
\end{tabularx}\\\vfill
